Power Analyses

### 2024-04-12 power_analyses.Rmd
reknitted manuscript removed unnecessary files

---
title: "Power Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
---

@@

## Detailed: Simple

@@

summary(reliability)
power_tab <- getPower(reliability)
power_80 <- findPower(power_tab, "N", 0.90)
power_80["HEX_HOH_SIN~~NFP_PHY"]
```

>>>>

---
title: "Power Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: show
    df_print: paged
---

@@

## Detailed

@@

summary(reliability)
power_tab <- getPower(reliability)
power_80 <- findPower(power_tab, "N", 0.90)
```

A power of 80% would imply collecting `r power_80[["HEX_HOH_SIN~~NFP_PHY"]]` participants.
